First of all, I would like to thank my family for their love and invaluable support, always making sure that my brain had the right amount of nutrients to work.

I would like to thank my advisors, Professor Ana Paiva and Professor Rui Prada, for their invaluable experience, expertise and guidance throughout the last year.

I'd also like to thank Tiago Ribeiro, Brian Ravenet, Sofia Petisca, Angelo Cafaro and Tobias Baur for their valuable support and prompt guidance during the development of this project. In addition, I would like to show my appreciation to Fraunhofer Institute for Integrated Circuits (IIS) and TELECOM ParisTech university for their collaboration on SHORE and GRETA, respectively.

A special thank you to my amazing friends, both inside and outside Instituto Superior Técnico, who provided the timely distractions and motivations. Special thanks to Nuno Xu for his invaluable collaboration during the development of the user studies, but, not the least, for being my friend. Another special thanks to Tiago Santos whose unique humour never fails to perplex me, always providing the right laugh at the right time. Special thanks to my closest friend Emanuel Lopes, who is currently doing his PhD and yet, took the time to review this document. In addition, in no particular order, I would like to thank Ana Apura, Frederico Sabino, Miguel Faria, Pedro Garcia, Joana Teixeira, Nuno Sousa, André Pires, and Rita Santos for being there for me.

Lastly, and not the least, this thesis would not be possible without my caring and loving girlfriend, Joana Pinto, who was always there for me and whose idiosyncratic stubbornness proved invaluable when reviewing the dissertation. 

Thank you.